---
title: "DATA 607 Assignment 9"
output: html_document
---

***Gehad Gad***

***March 28th, 2020***

***DATA 607 Assignment 9***


***Assignment instructions:***

The New York Times web site provides a rich set of APIs, as described here:  https://developer.nytimes.com/apis You’ll need to start by signing up for an API key. Your task is to choose one of the New York Times APIs, construct an interface in R to read in the JSON data, and transform it into an R DataFrame. 

```{r}
#Import libraries.
library(httr)
library(jsonlite)
library(jsonify)
library(rjson)
library(DT)
library(RCurl)
```

I used the most popular API from nytimes.

```{r}
#Import the data.

URL <- "https://api.nytimes.com/svc/mostpopular/v2/emailed/7.json?"

API_KEY <- "&api-key=apNn2DgbWnOCntVui5JfL15JLBRpJrXy"

NYURL <- paste(URL, API_KEY, sep = "")

NYTdata <- GET(NYURL)

DATA <- content(NYTdata, type = "text", encoding = "UTF-8")

```

#I tried to use fromJSON or Parse but both did not work for some reason. I learned about jsonify and it worked here.

```{r}

jsonify:: from_json(DATA)


```



